cardinalR: Generating interesting high-dimensional data structures

### 2025-10-08 paper-cardinalR.Rmd
Renumbered the sections
Updated branching projection

@@

## Usage

### Main function

@@

### Shape generators

@@

#### Branching

@@

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

#### Cone

@@

#### Cube

@@

#### Gaussian

@@

#### Linear

@@

#### Möbius

@@

#### Polynomial

@@

#### Pyramid

@@

#### S-curve

@@

#### Sphere

@@

#### Swiss Roll

@@

#### Trefoil knots

@@

#### Trigonometric

@@

### Generate a spherical or hyperspherical hole within a structure

@@

### Generate noise dimensions

@@

### Multiple cluster examples

@@

### Additional functions

>>>>

# Usage

@@

## Main function

@@

## Shape generators

@@

### Branching

@@

## First projection
projection <- cbind(
    c(-0.083573,-0.019043,0.006574,-0.035774),
    c(0.005380,0.068541,-0.030810,-0.054717))

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.8, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.085,
                                              axis_scaled = 6, 
                                              axis_pos_x = -0.055, 
                                              axis_pos_y = -0.055, 
                                              threshold = 0.006))

orglinearbranches_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.07, 0.07), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

### Cone

@@

### Cube

@@

### Gaussian

@@

### Linear

@@

### Möbius

@@

### Polynomial

@@

### Pyramid

@@

### S-curve

@@

### Sphere

@@

### Swiss Roll

@@

### Trefoil knots

@@

### Trigonometric

@@

## Generate a spherical or hyperspherical hole within a structure

@@

## Generate noise dimensions

@@

## Multiple cluster examples

@@

## Additional functions
